A new tidy data structure to support exploration and modeling of temporal data

### 2019-07-21 tsibble.Rmd
added reviews

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = 'figure/', fig.align = 'center', fig.show = 'hold', 
  cache = FALSE, cache.path = 'cache/', 
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
```

```{r external, include = FALSE}
read_chunk('scripts/demo.R')
read_chunk('scripts/flights.R')
read_chunk('scripts/smart-meter.R')
```

>>>>

```{r setup, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = 'figure/', fig.align = 'center', fig.show = 'hold', 
  cache = FALSE, cache.path = 'cache/', 
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
read_chunk('scripts/demo.R')
read_chunk('scripts/flights.R')
read_chunk('scripts/smart-meter.R')
```
